
% Thesis Abstract -----------------------------------------------------


%\begin{abstractslong}    %uncommenting this line, gives a different abstract heading
\begin{abstracts}        %this creates the heading for the abstract page

The resource management is no doubt one of the key problems that all clusters have to face. 
The LOFAR telescopes observe the sky and archive the records. 
Though there are computation facilities to process the observation data, the quantity of data is far beyond its capability of available computing facilities. 
Therefore, the data is fetched, and processed through a multiple-step pipeline when it is needed. 
Each step may take a long time, and consume significant amount of computation power. 
Currently, we have horizontal implementations in MPI and Spark,  where computation power follows the numbers of involved computing unit.
However, both of them have intrinsic drawback on resource utilizing. 
To promote the utilization of the resources, we propose an auto-provisioning distributed computing system. 
The auto-scaling mechanism enables the applications to dynamically fetch and release resources, and in the same time,  the resources of the cluster are used to the maximum extent. 
The results show that the nominal resource utilization of a cluster can be improved up to 99.9\%. 
With idle resources being used, users may take less time to wait. 
In our busy cluster scenario test case, users take 10\% less time on average to wait for the job to be finished at the submission of the jobs.


\end{abstracts}
%\end{abstractlongs}


% ---------------------------------------------------------------------- 
